% don't remove the folling lines, and edit the defintion of \main if needed
\documentclass[../report.tex]{subfiles}
\providecommand{\main}{..}
\IfEq{\jobname}{\currfilebase}{\AtEndDocument{\biblio}}{}
% until here

\begin{document}

\section{Di-Higgs production and Higgs self couplings\label{sec3:HH}}

The HL-LHC is expected to be a Higgs boson factory, and the study of the double-Higgs ($HH$) production is onw of the key goal of this high-luminosity program. Despite the small production cross-section compared to the single-Higgs boson production, more than 100000 $HH$ should be produced by the HL-LHC per experiment. The trilinear self-interaction of the Higgs boson is described by a with a coupling strength $\lambda_{HHH}  = \frac{m_H^2}{2v^2} $, where $m_H$ is the Higgs boson mass, and $v$ the electroweak symmetry breaking vacuum expectation value. Measurements of the Higgs trilinear interaction would provide constraints on the shape of the Higgs potential close to the minimum. and would allow to verify the electroweak symmetry breaking mechanism of the SM.
The existence of an extended scalar sector or the presence of new dynamics at higher scales could modify the Higgs boson self-couplings.
In the following the trilinear self-coupling strength, measured relative to the SM expectation is denoted by $\kappa_{\lambda} = \lambda_{HHH}/\lambda_{HHH}^{SM}$

This section describes the prospects for studies of the Higgs boson pair production at the HL-LHC and HE-LHC and is organised as follows: the state-of-the-art NLO computions of the Higgs boson pair production cross sections is shown in Section~\ref{sec:HH_NLO}. Section~\ref{sec:HH_meas_exp} describes the prospect experimental analyses with the ATLAS and CMS experiments with realistic conditions, while Section~\ref{sec:HH_meas_th} concentrates on alternative methods with phenomenology studies. Studies at the HE-LHC are shown in Section~\ref{sec:HH_HE} with both phenomenological and experimental perspectives. Indirect probes of the trilinear couplings are described in Section~\ref{sec:HH_indirect}, using differential cross-section measurements or global fits. Finally Section~\ref{sec:HH_implications} show the implications of the trilinear coupling measurements on b-physics and the electroweak phase transition.  

\subsection{NLO cross sections}
\label{sec:HH_NLO}

\subsubsection{SM Calculation}

\input{section3/HHotherChannels.tex}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%
%%%   subsection about variations of the trilinear coupling
%%%

\input{section3/lambda_var.tex}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 

%%%
%%%   nonlinear EFT subsection
%%%

\input{section3/nonlinearEFT.tex}

%%%%%%%%%%%%%%%%%%% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Double Higgs measurements and trilinear coupling: experimental prospects}
\label{sec:HH_meas_exp}

The current Run 2 measurements of the Higgs-boson-pair production are performed with approximately 36~$fb^{-1}$ of collision data at a centre-of-mass energy of 13~TeV, combining different decay channels~\cite{ATLAS-CONF-2018-043, Sirunyan:2018two}. 
The ATLAS collaboration reports the combined observed (expected) limit on the non-resonant Higgs-boson-pair production cross-section of 6.7 (10.4) times the SM expectation. The ratio of the Higgs boson self-coupling to its SM expectation is observed (expected) to be constrained at 95\% CL to $-5.0<\kappa_{\lambda}<12.1$ ($-5.8<\kappa_{\lambda}<12.0$). 
The reported combined observed (expected) limit on the non-resonant Higgs-boson-pair production cross-section by the CMS collaboration is 22.2 (12.8) times the predicted Standard Model cross-section. The ratio of the Higgs boson self-coupling to its SM expectation is observed (expected) to be constrained at 95\% CL to $-11.8<\kappa_{\lambda}<18.8$ ($-7.1<\kappa_{\lambda}<13.6$). 

Either those measurements were extrapolated to the centre-of-mass energy of 14~TeV and integrated luminosity of 3000~\ifb, either dedicated samples were used. Parameterised functions were used to estimate the response of the upgraded ATLAS and CMS detectors at the HL-LHC. The average number of additional proton-proton interactions (pile-up) per bunch crossing is assumed to be $<\mu>$ = 200.

Only the production of HH pairs through gluon-gluon fusion is considered, with an expected cross-section of 36.69$^{+2.1\%}_{-4.9\%}$ fb at 14 TeV~\cite{Grazzini:2018bsd}. The state of the art NNLO/NNLL calculation with finite top mass effects included at NLO in QCD is used, for a Higgs boson mass of 125 \UGeV. Scale uncertainties are reported as superscript/subscript. The estimated top quark mass uncertainty of the NNLOFTapprox predictions is also presented, together with PDF and $\alpha_{S}$ uncertainties. PDF uncertainties are estimated within the Born-improved approximation. The calculation is performed in the on-shell top quark mass scheme, and studies of the uncertainty related to the scheme choice are in progress. 

\subsubsection{Measurements with the ATLAS experiment}
\label{sec:HH_ATLAS}

\subfile{\main/section3/HHmeasurement_ATLAS}

\subsubsection{Measurements with the CMS experiment}
\label{sec:HH_CMS}

\input{section3/HHmeasurement_CMS.tex}

\subsubsection{Combination of measurements}
\label{sec:HH_Combination}

\subfile{\main/section3/HHmeasurement_Combination}

%%%%%%%%%%%%%%%%%%% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Double Higgs measurements and trilinear coupling: alternative methods}
\label{sec:HH_meas_th}

%%%%%%%%%%%%%%%%%%% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Prospects for $hh \to (b \bar b)(WW^*) \to (b \bar b)( \ell^+\ell^- \nu_\ell \bar\nu_\ell)$}
\subfile{\main/section3/bbWW}



%%%%%%%%%%%%%%%%%%% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsubsection{Prospects for $bb\gamma\gamma $: Bayesian optimization and BDT}

\subfile{\main/section3/HHbbgammagamma}

%%%%%%%%%%%%%%%%%%% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


%%%%%%%%%%%%%%%%%%% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%






\subsection{HE-LHC prospects}
\label{sec:HH_HE}

\subsubsection{Theory studies}
\subfile{\main/section3/HEproj_theory}

\subsubsection{ATLAS studies}
\subfile{\main/section3/HH_HE-LHC_ATLAS}

%%%%%%%%%%%%%%%%%%% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\subsection{Indirect probes}
\label{sec:HH_indirect}

In this section we discuss the possibility of indirectly extract information on the trilinear self interaction of the Higgs boson via precise measurements of single-Higgs production~\cite{McCullough:2013rea,Gorbahn:2016uoy,Degrassi:2016wml,Bizon:2016wgr,DiVita:2017eyz,Barklow:2017awn,Maltoni:2017ims,DiVita:2017vrr,Maltoni:2018ttu} at the HL-LHC and HE-LHC. This strategy is complementary to the direct measurement via double-Higgs production, which already at leading order,~i.e.~at one loop in the case of $gg \to HH$, depends on the trilinear Higgs self interaction. In the case of single-Higgs production, on the contrary, the Higgs self interactions enter only via one-loop corrections, i.e., at the two-loop level for the gluon-fusion ($ggF$) production mode. The effects of modified Higgs self interactions are therefore generically much smaller, but for single-Higgs production processes the precision of the experimental measurements is and will be much better than for double-Higgs production. This, and the fact that for single-Higgs production many different final states and both inclusive as well as  differential measurements are possible will lead to competitive indirect determinations of the trilinear Higgs self coupling. In \cite{Degrassi:2017ucl,Kribs:2017znd} also electroweak precision observables have been considered to this purpose.

\subsubsection{Indirect probes through single Higgs boson production}

\subfile{\main/section3/HL-HE-tril_indirect_computation}

\subsubsection{Indirect probes of the trilinear coupling through differential distributions measurements}

\subfile{\main/section3/HL_CMS_FTR_18_020}


\subsubsection{Global fit}
\label{sec:HH_Global_fit}
\subfile{\main/section3/HL-HE-tril_indirect_globalfit}

\subsection{Implications of the HH measurements}
\label{sec:HH_implications}

\subsubsection{Implications for flavor models}
\input{\main/section3/dihiggs_flavor}


\subsubsection{Implications for theories of electroweak phase transition}
\input{\main/section3/HELHC_EWPT}


\end{document}
